Stage-structured evolutionary demography for simultaneous hermaphrodites with partial selfing

### 2020-09-01 notes/notes-SA-partSelf-wDemography.tex
fixed zeta typo in notes

{
\footnotesize
 \begin{align*} \label{eq:M22}
	\mbf{M}_{22} = 
		\frac{1}{\lambda_{AA}}\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \numberthis
\end{align*}
}
where 
\begin{equation}
  \mbox{p}_{n}=\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \left( \hat{\mathbf{p}}^S_{AA}+\hat{\mathbf{p}}^X_{AA} \right)	
\end{equation}

@@

{
\footnotesize
\begin{align*} \label{eq:eigAA}
	\tilde{\zeta}_{AA} = 
		\frac{1}{\lambda_{AA}}\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right). \numberthis
\end{align*}
}

@@

{\footnotesize
\begin{equation} \label{eq:coexist_AA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \\ 
\end{equation}

\begin{equation} \label{eq:coexist_AA}
	\lambda_{aa} < 
			\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{AA})\mbf{F}_{AA}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{AA} +C_{AA} (1 - \delta) \mbf{F}_{AA}  \\ 
			\end{array} \right), \\ 
\end{equation} 
}

>>>>

{
\footnotesize
 \begin{align*} \label{eq:M22}
	\mbf{M}_{22} = 
		\frac{1}{\lambda_{AA}}\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa} + \Theta\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \numberthis
\end{align*}
}
where $\Theta = \mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{aa}^\prime$, and

\begin{equation}
  \mbox{p}_{n}=\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \left( \hat{\mathbf{p}}^S_{AA}+\hat{\mathbf{p}}^X_{AA} \right)	
\end{equation}

@@

{
\footnotesize
\begin{align*} \label{eq:eigAA}
	\tilde{\zeta}_{AA} = 
		\frac{1}{\lambda_{AA}}\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa} + \Theta\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right). \numberthis
\end{align*}
}

@@

{\footnotesize
\begin{equation} \label{eq:coexist_AA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa} + \Theta\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \\ 
\end{equation}

\begin{equation} \label{eq:coexist_aa}
	\lambda_{aa} < 
			\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{AA})\mbf{F}_{AA} + \Phi\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{AA} + C_{AA} (1 - \delta) \mbf{F}_{AA}  \\ 
			\end{array} \right), \\ 
\end{equation} 
}

where $\Phi = \mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{AA}^\prime$.
